\documentclass{uva_bachelor_thesis}
\usepackage{hyperref} % for bibtex urls
\usepackage{csquotes} % for quotes
\usepackage[acronym]{glossaries} % acronyms 
\usepackage{subcaption} % side by side subfigures
\usepackage{newclude} % include without page break
\usepackage{minted} % code listings
\usepackage[numbers]{natbib} % apa refs with numbers
\usepackage{booktabs} % better tables
\usepackage{tabularx}
\usepackage{soul} % highlighting
\usepackage{float}
\usepackage[justification=centering]{caption}
\usepackage{spverbatim}

\definecolor{Light}{gray}{.92}
\sethlcolor{Light}

\let\OldTexttt\texttt
\renewcommand{\texttt}[1]{\OldTexttt{\hl{#1}}}
\newcommand{\bfttt}[1]{\OldTexttt{\bf{#1}}}

\newminted{java}{fontsize=\tiny, frame=lines, bgcolor=LightGray!18} % define code listing

\usepackage{tikz}
\usetikzlibrary{positioning,%
  shapes.geometric,%
  shapes.misc,%
  calc,%
  fit,%
  decorations,%
  decorations.pathreplacing,%
  backgrounds,%
  arrows,%
  automata,%
  trees%
}

\xdefinecolor{bordeaux}{RGB}{128,0,50}
\xdefinecolor{niceblue}{RGB}{13,41,79}
\xdefinecolor{nicegreen}{RGB}{13,79,18}
\xdefinecolor{niceviolet}{RGB}{79,13,74}
\colorlet{maincolor}{niceviolet}
\colorlet{alertedcolor}{red}
\colorlet{examplecolor}{green!50!black}

\usepackage{etoolbox}
\appto\appendix{\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}}

% reinstate the correct level for list of tables and figures
\appto\listoffigures{\addtocontents{lof}{\protect\setcounter{tocdepth}{1}}}
\appto\listoftables{\addtocontents{lot}{\protect\setcounter{tocdepth}{1}}}

% Enumerated quotes
\newcounter{quotecount}
\newcommand{\MyQuote}[1]{\vspace{1.5em}\refstepcounter{quotecount}%
     \parbox{10cm}{\em \textit{#1}}\hspace*{2cm}(\arabic{quotecount})\\[1em]}

% Glossary items
\makeglossaries
\newacronym{gui}{GUI}{graphical user interface}
\newacronym{mvc}{MVC}{model-view-controller}
\newacronym{rest}{REST}{representational state transfer}
\newacronym{ddd}{DDD}{domain-driven design}
\newacronym{no}{NO}{Naked Objects}
\newacronym{goms}{GOMS}{Goals, Operators, Methods and Selection rules}

% Title Page
\title{CLIsis: An Interface for Visually Impaired Users of Apache Isis Applications}
\author{Sander Ginn}
\supervisors{Maarten Marx (UvA), Dan Haywood (Apache)}

\begin{document}
\maketitle

\begin{abstract}
The vast majority of modern user interfaces are graphical user interfaces. This is problematic for users who are visually impaired, as screen reading technology does at best a mediocre job at making graphical user interfaces accessible to these users. This thesis proposes a content unaware user interface for applications developed with Apache Isis that represents information through audio feedback. We took a three-stage approach to perform the adaptation, ensuring that the new user interface offers identical functionality as the graphical user interface. In order to evaluate how user performance is affected when using the new user interface, the GOMS method was used to analyse tasks in both user interfaces. We then performed a series of tests with test subjects and compared the results to the GOMS analysis. We conclude that it is possible to adapt a graphical user interface so that visually impaired users can interact with the application. Furthermore, we pose several suggestions to improve the results.
\end{abstract}

\tableofcontents

\input{introduction}
\input{theoreticalbackground}
\input{methods}
\input{implementation}
\input{evaluation}
\input{conclusion}
\bibliographystyle{apa}
\bibliography{bibliography/bibliography}
%\nocite{*}

\printglossaries
\input{appendices}

\end{document}